R Notebook

### 2022-04-12 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

```{r acquire_and_format_data}
deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R', "DeaminationAnalysis.R"))

@@

```{r plot_6-4_tandem_C>T_pos_frequency}
for (i in 1:length(sixFourTandemCTMismatches)) {
  for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
    plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
                                    title = paste("CPD", names(sixFourTandemCTMismatches)[i], 
                                                  names(sixFourTandemCTMismatches[[i]])[j], 
                                                  "Tandem C>T Mismatch Pos"))
  }
}
```

>>>>

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R', "DeaminationAnalysis.R"))
source(file.path(bioinformaticsDirectory, "Chromatin_Features_Analysis", "R_scripts", "PeriodicityAnalysis.R"))
```

```{r acquire_and_format_data_1}
deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")

@@

```{r plot_6-4_tandem_C>T_pos_frequency}
for (i in 1:length(sixFourTandemCTMismatches)) {
  for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
    plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
                                    title = paste("6-4", names(sixFourTandemCTMismatches)[i], 
                                                  names(sixFourTandemCTMismatches[[i]])[j], 
                                                  "Tandem C>T Mismatch Pos"))
  }
}
```

```{r acquire_and_format_data_2}
load(file.path(deaminationDataDirectory, "deamination_periodicity_results.rda"))
dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))

```{r periodicity_stats}
print(mutperiodData$periodicityResults)
```

```{r CPD_rotational_periodicity_trinuc_normalized}
parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
                        title = "CPD 1hr Rep1 Rotational Trinuc Norm")
parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
                        title = "CPD 24hr Rep1 Rotational Trinuc Norm")
parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
                        title = "CPD 48hr Rep1 Rotational Trinuc Norm")
```

```{r CPD_rotational_periodicity_XR-seq_normalized}
parseAndPlotPeriodicity(
  dataSetNames$NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
  title = "CPD 1hr Rep1 Rotational XR-seq Norm")
parseAndPlotPeriodicity(
  dataSetNames$NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
  title = "CPD 24hr Rep1 Rotational XR-seq Norm")
parseAndPlotPeriodicity(
  dataSetNames$NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
  title = "CPD 48hr Rep1 Rotational XR-seq Norm")
```

```{r CPD_translational_periodicity_trinuc_normalized}
parseAndPlotPeriodicity(
  dataSetNames$`NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
  title = "CPD 1hr Rep1 Rotational Trinuc Norm")
parseAndPlotPeriodicity(
  dataSetNames$`NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
  title = "CPD 24hr Rep1 Rotational Trinuc Norm")
parseAndPlotPeriodicity(
  dataSetNames$`NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
  title = "CPD 48hr Rep1 Rotational Trinuc Norm")
```

```{r CPD_translational_periodicity_XR-seq_normalized}
parseAndPlotPeriodicity(
  dataSetNames$`NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
  title = "CPD 1hr Rep1 Rotational XR-seq Norm")
parseAndPlotPeriodicity(
  dataSetNames$`NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
  title = "CPD 24hr Rep1 Rotational XR-seq Norm")
parseAndPlotPeriodicity(
  dataSetNames$`NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
  title = "CPD 48hr Rep1 Rotational XR-seq Norm")
```
